The 2014 SMT Competition

### 2015-08-04 2014/report/SMTCOMP.tex
Fixed outline

In the succeeding sections we describe the context of the competition (\S\ref{sec:context}), its goals and organization (\S\ref{sec:goals}), procedure (\S\ref{sec:procedure}), participants (\S\ref{sec:participants}), benchmarks (\S\ref{sec:benchmarks}), computational infrastructure (\S\ref{sec:starexec}), results (\S\ref{sec:results}), the place of SMT-COMP in the FLoC Olympic Games (\S\ref{sec:floc}), and post-competition activities (\S\ref{sec:post}). Section \ref{sec:conclusions} presents observations on this competition and recommendations for the future.

\davidc{Correct the outline}

>>>>

In the succeeding sections we describe 
the competition goals (\S\ref{sec:goals}), 
the SMT-LIB language that is the basis for the competition (\S\ref{sec:context}), 
the competition benchmarks (\S\ref{sec:benchmarks}), 
participants (\S\ref{sec:participants}), 
procedure (\S\ref{sec:procedure}),
computational infrastructure (\S\ref{sec:starexec}), 
comparisons with other competitions (\S\ref{sec:OtherCompetitions}), 
the results (\S\ref{sec:results}), 
the place of SMT-COMP in the FLoC Olympic Games (\S\ref{sec:floc}), 
and post-competition activities (\S\ref{sec:post}). 
Section \ref{sec:conclusions} presents observations on this competition and recommendations for the future.
